Leveraging Diversity to Find Bugs\\ in JavaScript Engines

### 2018-08-22 paper/paper.tex
pass on results

This section reports results of test transplantation. We analyzed the
failures observed when running a test suite original from a given
engine in another engine. Intuitively, we want to assess how promising
is to use knowledge of developers of a given engine to find bugs in a
different engine.

Table~\ref{tab:cross-testing} shows the number of failures observed
for each pair of test suite and engine. The first column shows the
test suites and the first row shows the engines that run those
tests. We use a dash (``-'') to indicate that we did not consider the
combinations that associate a test suite with its parent engine;
failures in those cases would either indicate regressions or flaky
tests as opposed to unknown bugs for that engine. We did not run test
cases that fail on its parent engine in any other engines; we wanted
all tests to pass on their parent engine as that would indicate that
the test case is coherent and can be used. In total, 64 test cases
were discarded for that reason--6 from \jsc{} and 57 from
\smonkey. Furthermore, we required that a test does not manifest
compile errors as we want to focus on bugs in code not in tests. For
that reason, we used the tests listed under the column
``compile-in-all'' from Table~\ref{tab:test-suites}, totalling
\totalTestFilesCompileInAll{} cases. \Mar{can you confirm that we used
  ``compile-in-all'' and not ``origina'' as these numbers
  suggest?}\Fix{In total, 7,029 test files (\ie{}, 38369-31276-64)
  were considered in this experiment, which involved 24,922 test runs
  (\ie, (7029*4)-1021-57-2116).}  Of these, 812 failures were
manifested (3.25\% of the runs) across \textbf{543} distinct files
(7.72\% of the files). A developer with experience in \js\ analyzed
each of these files in separate as to classify if the failure was
fault-revealing or not (\ie{}, a false positive).  We observed from
the table that, considering this dataset, the Mozilla \smonkey\ was
the engine that failed the least whereas the Microsoft engine
\chakra\ failed the most. The \smonkey\ test suite also revealed more
failures than any other, as expected, considering that it is the suite
with more tests (see Table~\ref{tab:test-suites}).

@@

The piecharts from Figure~\ref{fig:piecharts-transplantation} show the
distribution of false and true positives in this experiment. The
piechart at the top shows false alarms. The absolute number of tests
in each category is shown in parentheses to the right-side of each
slice label, which names the source of false positive. The sources of
false positives are as follows:

@@

\begin{itemize}
  \item \textbf{Undefined Behavior.} False positives of this kind are
    manifested when tests cover implementation-dependent behavior, as
    defined in the ECMA262 specification~\cite{ecmas262-spec}. For
    example, one of the tests from \jerry\ uses the function
    \CodeIn{Number.toPrecision([precision])}, which translates a
    number to a string, considering a given number of significant
    digits. The floating-point approximation of the real value is
    implementation-dependent, making the test to pass only in
    \chakra\ for that test. As another example, some tests from
    \Fix{Y} use the implementation-dependent description message\Mar{what is the
      name of the property?} encapsulated in an \CodeIn{Error} object
    in assertions. As such, those tests fail in all engines but \Fix{Y}.

  \item \textbf{Timeout/OME\footnote{ome is for out of memory
      error.}.} False positives of this kind manifest because the
    engine that runs the test does not optimize the code as the
    original engine and that has an effect in the test outcome.  The
    test may fail to finish at the specified time budget or it exceeds
    the memory budget. For example, a test case from the \jsc{} suite
    defines a function with a tail-call recursion. The test fails in
    all engines but \jsc{}, which implements tail-call optimization,
    which enables the test to finish execution fast.

  \item \textbf{Not implemented.} False positives of this kind
    manifest when a test fails because it covers a function that is
    part of the official spec, but is not implemented in the target
    engine yet. For example, at the time of writing, \chakra{} does
    not implement by default various properties from the
    \mcodeid{Symbol} object. These properties are only available
    activating the ES6 experimental mode with the flag
    \CodeIn{-ES6Experimental}.

  \item \textbf{Unknown.} This category includes the cases we were
    unable to confidently diagnose the failure but we suspected it was
    a false alarm.

\end{itemize}

We observed that ``Unknown'' and ``Undefined'' were the most
predominant sources of false positives. Considering true positives, we
found a reasonable number of duplicate reports, but not enough high to
justify attempting to automate the detection of duplicates.

@@

Table~\ref{tab:test-transplantation-bugs} lists all bugs we found
with test transplantation. The first column shows the identifier we
assigned to the bug, column ``Date'' shows the date the bug was
reported in the format ``m/dd'', column ``Engine'' shows the affected
engine, column ``Status'' indicates the status of the bug report at
the time of the writing (\eg{},``New'', ``Rejected'', ``Confirmed'',
''Fixed''), column ``Url'' shows the web address for the
bug report entry in the bug tracking system (de-anonymized upon request), column
``Severity'' shows the severity level for confirmed bugs, and,
finally, column ``Suite'' shows the name of the engine that originated
the test.

Considering severity levels, it is important to note that \jsc{} uses
five levels~\cite{jsc-severity} whereas
\chakra{}~\cite{chakra-severity} and
\smonkey{}~\cite{mozilla-severity} use only two. As usual, the
smallest the severity value the highest the severity of the bug. We
use a dash (``-'') as the severity level for bugs with pending
confirmation.  No bug we reported in this experiment was rejected.  Of
the \Fix{17} bugs we reported in this experiment, \Fix{9} were
analyzed and moved from the status ``New'' to ``Confirmed''. Of these,
\Fix{8} are severity-2 bugs.  \chakra{} was the engine with the
highest number of confirmed bugs, \Fix{8} in total, with \Fix{1} bug
fixed. Considering the remaining engines, \veight{} confirmed one
bug. Curiously, Google engineers confirmed that report in a few
hours. We found that development teams of other engines, specially
\jsc\, took much longer to analyze bug reports as can be observed by
some pending reports from April 2018. Although we did not find any
showstopper critical bugs, most of the bugs are seemingly important as
per the categorization given by engineers. Analyzing the issue tracker
of \chakra, we found that severity-1 bugs are rare.

Overall, we found these results promising given that precision (\ie{}
the ratio of true positives over all reports) needs to take into
account the cost of inspecting the warning~\cite{harman-ohearn-2018};
it took a week for the developer to inspect the set of warnings
entirely. The precision for \jsc\ was \Fix{X\%} (\ie, XX/270), which
seems a low rate, but it took approximately \Fix{x} days to find
\Fix{y} real bugs on this engine. Section~\ref{sec:bugs} show samples
of false and true positives.

@@

\subsubsection{Methodology}
The methodology we used to assess effectiveness of this technique is
as follows. To avoid experimental noise, we only fuzz test files that
pass in all engines.  This corresponds to the tests appearing under
the column ``no-fail-in-all'' from Table~\ref{tab:test-suites}--a
total of \totalTestFilesPassInAll\ tests satisfy this restriction.
The intuition is that we wanted to avoid the scenario where fuzzing
produces a fault-revealing input based on a test that was already
revealing failures on some engine. This decision ensures that we can
establish cause-effect relationship between fuzzing and the
observation of discrepancy.

\vspace{1ex}
\noindent\textbf{Exploratory Phase.} For the first three months of the
study, our inspection process was exploratory.  In this phase, we
wanted to learn whether or not black-box fuzzers could reveal real
bugs and how effective \lo\ warnings were relative to
\hi\ warnings. Considering the choice of fuzzers, we did find several
bugs with \radamsa\, but only some with \quickfuzz. The rationale for
studying the the \hi\ and \lo\ warning classification was that if we
found that the ratio of bugs from \lo\ warnings was rather low, we
could focus our inspection efforts only on \hi\ warnings as we
expected the number of warnings to increase dramatically compared to
the previous experiment. That finding would be important to reduce
inspection cost and guide future developments of this approach. To run
this experiment, we trained eight students in analyzing the warnings
that our infrastructure produces. The students were enrolled in a
graduate-level testing class. We listed warnings in a spreadsheet and
requested the students to update an ``owner'' column indicating who
was working on it, but we did not enforce a strict order on the
warnings the students should inspect. Recall from
Section~\ref{sec:clusterization} that we clustered \lo\ warnings in
buckets. For that reason, we only listed one \lo\ warning per
representative class/bucket in the spreadsheet. First, we explained,
through examples, the possible sources of false alarms they could find
and then we asked the students to use the following procedure when
finding a suspicious warning. Analyze the parts of the spec related to
the problem and, if still suspicious, look for potential duplicates on
the bug tracker of the affected engine using related keywords. If none
was reported, indicate in the spreadsheet that that warning is
potentially fault-revealing. We encouraged students to use
lithium~\cite{lithium} to minimize long test cases; the tests from the
Mozilla suite are often longer than others. Only after the co-authors
checked the potential bugs, a bug report was filed. Each student found
at least one bug using this methodology.

\vspace{1ex}
\noindent\textbf{Non-Exploratory Phase.} Results obtained in the
exploratory phase confirmed our expectations that most of the bugs
found during the initial three months of investigation were related to
\hi\ warnings. For that reason, we changed our inspection
strategy. This time, only the co-authors inspected the bugs using a
similar discipline as before. However, the set of warnings inspected
and the order of inspection changed. We restricted our analysis to
\hi\ warnings and, aware that we would be unable to analyze each and
every warning reported, we grouped those warnings per engine,
analyzing each group in a round-robin fashion.  At each iteration, we
analyzed \Fix{five} warnings in each group. A warning belongs to the
group of a given engine if only that engine manifests distinct
behavior, \ie{}, it produces a distinct output compared to others. We
separated in a distinct group the warnings for which two engines
diverge. The rationale for this methodology was to give attention to
each engine more uniformly, enabling more fair comparison across
engines.

\subsubsection{Results} In this section we discuss results obtained
across these two phases of the experiment. Table~\ref{tab:summary-lo}
shows statistics of \lo\ warnings obtained when fuzzing inputs with
different tools. Column ``\# buckets'' shows the number of buckets
associated with ``\lo'' warnings, column ``\# files'' shows the total
number of files involved in these warnings, and column ``avg. \# files
per bucket'' show the average number of files per bucket. Note that
the difference of files per bucket across fuzzers was not very
significant.

@@

Table~\ref{tab:summary-hi} shows statistics for \hi\ warnings; recall
from Section~\ref{sec:clusterization} that we do not cluster
\hi\ warnings\Comment{ as there was no clear clustering criteria to
  use for that}. This table breaks down \hi\ warning by the affected
engine, \ie, the engine manifesting a distinct output among those
analyzed. Column ``+1'' show the cases where more than one engine
disagree on the output. Note that the ordering of engines considering
this metric is consistent with the one observed on
Table~\ref{tab:cross-testing}, with \chakra\ and then \jsc\ associated
with more warnings/failures compared to other engines.
%\veight\ and \smonkey.

@@

Table~\ref{tab:false-positives} shows the distribution of false
positives per source. A false positive is a bucket that did not lend
itself in a bug report. The sources of imprecision are as defined in
Section~\ref{sec:transplantation} with the addition of two new
sources, which we did not observe before. The source ``Invalid Input''
indicates that the test violated some part of the specification. For
example, the test indirectly invoked some function with unexpected
arguments\Fix{provide concrete example}. The source ``Upcoming
Feature'' indicates that the test fails because it uses a feature that
is available in the original engine, but it is still not standard, and
the target engine does not support that feature. For example,
\Fix{provide concrete example}

\begin{table}[h]
  \centering
  \caption{\label{tab:false-positives}Distribution of false
    positives buckets per source.}
  \begin{tabular}{crr}
    \toprule
    & \radamsa\ & \quickfuzz\ \\
    Undefined & 18 & - \\
    Timeout/OME & 23 & - \\
    Not Implemented & 19 & - \\
    Upcoming Feature & - & - \\
    Error Message Mismatch & 3 & - \\    
    Invalid Input & 10 & - \\    
    \bottomrule     
  \end{tabular}
\end{table}

Table~\ref{tab:bugs} shows the list of bugs we reported with
differential testing across five months of analysis. The table is
organized in two sections. The top section shows results obtained
during the exploratory phase of the study and the bottom section shows
the results obtained during the non-exploratory phase. The table shows
the date the bug was reported (``Date''), the fuzzing tool used to
detect the bug (``Fuzz''), the \js\ engine affected (``Engine''), the
status of the bug report as of Aug. 24, 2018 (``Status''), the Url of
the bug report (``Url''), the severity of the bug report
(``Severity''), the priority that we assigned to the warning that
revealed the bug (``Priority''), and the test suite from the original
test input (``Suite'').

\Mar{REVISE}So far, ten of the bugs we
reported were confirmed, two of which were fixed. One bug report we
submitted was rejected on the basis that the offending JS file
manifested an expected incompatibility across engine implementations.
Note from the table that all bug reports still waiting for
confirmation are associated with the \jsc{} engine (JSC). A closer
look at the JSC issue tracker showed that the triage process is very
slow for that engine.  \Igor{ The bugs reported on \chakra{}'s bug
  tracker was defined as confirmed, however the bugs are included on a
  milestone for the next release following an internal priority.  } As
of now, we did not find any new bug on \smonkey{} and V8; the bugs we
found were duplicates and were not reported. Finally, it is worth
noting that \Fix{11 of the 19} JS files that manifested discrepancies
were \emph{not} produced with fuzzing (column ``Fuzz''). These are
test files from suites of different engines. This observation
emphasizes the importance of continuously collecting test suites from
multiple sources; today, we use test suites from seven different open
source engines, including a total of 30K test files.

>>>>

This section reports results of test transplantation. More
specifically, we analyzed the failures observed when running a test
suite original from a given engine in another engine. Intuitively, we
want to assess how effective is the idea of cross-fertilization of
knowledge among \js\ developers.

\vspace{0.5ex}
\subsubsection{Methodology}
\label{sec:methodology}
In this experiment we analyzed each failure observed in a test
execution. A developer with experience in \js\ analyzed each files in
separate and classified the failure as potentially fault-revealing or
not (\ie{}, a false positive). The co-authors supervised the
classification process as to validate correctness. For the cases the
developer classified the failures as potentially fault-revealing, one
of the co-authors carefully inspected the case and reported the bug
(or re-classified the failure as a false alarm).

\vspace{0.5ex}
\subsubsection{Results}
\label{sec:results}

Table~\ref{tab:cross-testing} shows the number of failures observed
for each pair of test suite and engine. The first column shows the
test suites and the first row shows the engines that run those
tests. We use a dash (``-'') to indicate that we did not consider the
combinations that associate a test suite with its parent engine;
failures in those cases would either indicate regressions or flaky
tests as opposed to unknown bugs for that engine. We did not run test
cases that fail on its parent engine in any other engines; we wanted
all tests to pass on their parent engine as that would indicate that
the test case is coherent and can be used. In total, 64 test cases
were discarded for that reason--6 from \jsc{} and 57 from
\smonkey. Furthermore, we required that a test does not manifest
compile errors as we want to focus on bugs in code not in tests. For
that reason, we used the tests listed under the column
``compile-in-all'' from Table~\ref{tab:test-suites}, totalling
\totalTestFilesCompileInAll{} cases. \Mar{can you confirm that we used
  ``compile-in-all'' and not ``origina'' as these numbers
  suggest?}\Fix{In total, 7,029 test files (\ie{}, 38369-31276-64)
  were considered in this experiment, which involved 24,922 test runs
  (\ie, (7029*4)-1021-57-2116).}  Of these, 812 failures were
manifested (3.25\% of the runs) across \textbf{543} distinct files
(7.72\% of the files). We observed from
the table that, considering this dataset, the Mozilla \smonkey\ was
the engine that failed the least whereas the Microsoft engine
\chakra\ failed the most. The \smonkey\ test suite also revealed more
failures than any other, as expected, considering that it is the suite
with more tests (see Table~\ref{tab:test-suites}).

@@

The sources of false positives found in this experiment are as
follows: \textbf{Undefined Behavior.} False positives of this kind are
manifested when tests cover implementation-dependent behavior, as
defined in the ECMA262 specification~\cite{ecmas262-spec}. For
example, one of the tests from \jerry\ uses the function
\CodeIn{Number.toPrecision([precision])}, which translates a number to
a string, considering a given number of significant digits. The
floating-point approximation of the real value is
implementation-dependent, making the test to pass only in \chakra\ for
that test. As another example, some tests from \Fix{Y} use the
implementation-dependent description message\Mar{what is the name of
  the property?} encapsulated in an \CodeIn{Error} object in
assertions. As such, those tests fail in all engines but
\Fix{Y}. \textbf{Timeout/OME\footnote{ome is for out of memory
    error.}.} False positives of this kind manifest because the engine
that runs the test does not optimize the code as the original engine
and that has an effect in the test outcome.  The test may fail to
finish at the specified time budget or it exceeds the memory
budget. For example, a test case from the \jsc{} suite defines a
function with a tail-call recursion. The test fails in all engines but
\jsc{}, which implements tail-call optimization, which enables the
test to finish execution fast. \textbf{Not implemented.} False
positives of this kind manifest when a test fails because it covers a
function that is part of the official spec, but is not implemented in
the target engine yet. For example, at the time of writing, \chakra{}
does not implement by default various properties from the
\mcodeid{Symbol} object. These properties are only available
activating the ES6 experimental mode with the flag
\CodeIn{-ES6Experimental}. \Mar{revise this.}\textbf{Unknown.} This
category includes the cases we were unable to confidently diagnose the
failure but we suspected it was a false alarm.

@@

The piecharts from Figure~\ref{fig:piecharts-transplantation} show the
distribution of false and true positives in this experiment. The
piechart at the top shows false alarms. The absolute number of tests
in each category is shown in parentheses to the right-side of each
slice label naming the source of false positive.  We observed that
``Unknown'' and ``Undefined'' were the most predominant
sources. Considering true positives, we found a reasonable number of
duplicate reports, but not enough high to justify attempting to
automate the detection of duplicates.

@@

Table~\ref{tab:test-transplantation-bugs} lists all bugs we found with
test transplantation. The first column shows the identifier we
assigned to the bug, column ``Date'' shows the date the bug was
reported in the format ``m/dd'', column ``Engine'' shows the affected
engine, column ``Status'' indicates the status of the bug report at
the time of the writing (\eg{},``New'', ``Rejected'', ``Confirmed'',
''Fixed''), column ``Url'' shows the web address for the bug report
entry in the bug tracking system (de-anonymized upon request), column
``Severity'' shows the severity level for confirmed bugs, and,
finally, column ``Suite'' shows the name of the engine that originated
the test. Considering severity levels, it is important to note that
\jsc{} uses five levels~\cite{jsc-severity} whereas
\chakra{}~\cite{chakra-severity} and
\smonkey{}~\cite{mozilla-severity} use only two. As usual, the
smallest the severity value the highest the severity of the bug. We
use a dash (``-'') as the severity level for bugs with pending
confirmation.  No bug we reported in this experiment was rejected.  Of
the \Fix{17} bugs we reported in this experiment, \Fix{9} were
analyzed and moved from the status ``New'' to ``Confirmed''. Of these,
\Fix{8} are severity-2 bugs.  Although we did not find any showstopper
critical bugs, most of the bugs are seemingly important as per the
categorization given by engineers. Analyzing the issue tracker of
\chakra, we found that severity-1 bugs are rare. Considering the bugs
confirmed by developers, \chakra{} was the engine with the highest
number, \Fix{8} in total, with \Fix{1} bug fixed. Considering the
remaining engines, \veight{} developers confirmed \Fix{one} bug we
reported. Curiously, Google engineers confirmed that report in a few
hours. We found that development teams of other engines, specially
\jsc\, took much longer to analyze bug reports as can be observed by
some pending reports from April 2018.

Overall, we found these results promising given that precision (\ie{},
the ratio of true positives over all reports) needs to take into
account the cost of inspecting the failure~\cite{harman-ohearn-2018};
it took a week for the developer to inspect the entire set of
failures. The precision for \jsc\ was \Fix{X\%} (\ie, XX/270), which
seems a low rate, but it took approximately \Fix{x} days to find
\Fix{y} real bugs on this engine. Section~\ref{sec:bugs} shows samples
of false and true positives.

\begin{center}
  \fbox{
    \begin{minipage}{8cm}
      \textit{Summary:}~Test transplantation is effective at finding
      functional bugs. Although the inspection cost is non-negligible,
      the approach was able to reveal several bugs in widely popular
      engines.
      \end{minipage}
    }
\end{center}

@@

\vspace{0.5ex}
\subsubsection{Methodology}
The methodology we used to assess effectiveness of this technique is
as follows. To avoid experimental noise, we only fuzz test files that
pass in all engines.  This corresponds to the tests appearing under
the column ``no-fail-in-all'' from Table~\ref{tab:test-suites}--a
total of \totalTestFilesPassInAll\ tests satisfy this restriction.
The intuition is that we wanted to avoid the scenario where fuzzing
produces a fault-revealing input based on a test that was already
revealing failures on some engine. This decision ensures that we can
establish cause-effect relationship between fuzzing and the
observation of discrepancy.

\vspace{0.5ex}
\noindent\textbf{Exploratory Phase.} For the first three months of the
study, our inspection process was exploratory.  In this phase, we
wanted to learn whether or not black-box fuzzers could reveal real
bugs and how effective \lo\ warnings were relative to
\hi\ warnings. Considering the choice of fuzzers, we did find several
bugs with \radamsa\, but only some with \quickfuzz. The rationale for
studying the the \hi\ and \lo\ warning classification was that if we
found that the ratio of bugs from \lo\ warnings was rather low, we
could focus our inspection efforts only on \hi\ warnings as we
expected the number of warnings to increase dramatically compared to
the previous experiment. That finding would be important to reduce
inspection cost and guide future developments of this approach. To run
this experiment, we trained eight students in analyzing the warnings
that our infrastructure produces. The students were enrolled in a
graduate-level testing class. We listed warnings in a spreadsheet and
requested the students to update an ``owner'' column indicating who
was working on it, but we did not enforce a strict order on the
warnings the students should inspect. Recall from
Section~\ref{sec:clusterization} that we clustered \lo\ warnings in
buckets. For that reason, we only listed one \lo\ warning per
representative class/bucket in the spreadsheet. First, we explained,
through examples, the possible sources of false alarms they could find
and then we asked the students to use the following procedure when
finding a suspicious warning. Analyze the parts of the spec related to
the problem and, if still suspicious, look for potential duplicates on
the bug tracker of the affected engine using related keywords. If none
was reported, indicate in the spreadsheet that that warning is
potentially fault-revealing. We encouraged students to use
lithium~\cite{lithium} to minimize long test cases; the tests from the
Mozilla suite are often longer than others. Only after the co-authors
checked the potential bugs, a bug report was filed. Each student found
at least one bug using this methodology.

\vspace{0.5ex}
\noindent\textbf{Non-Exploratory Phase.} Results obtained in the
exploratory phase confirmed our expectations that most of the bugs
found during the initial three months of investigation were related to
\hi\ warnings. For that reason, we changed our inspection
strategy. This time, only the co-authors inspected the bugs using a
similar discipline as before. However, the set of warnings inspected
and the order of inspection changed. We restricted our analysis to
\hi\ warnings and, aware that we would be unable to analyze each and
every warning reported, we grouped those warnings per engine,
analyzing each group in a round-robin fashion.  At each iteration, we
analyzed \Fix{five} warnings in each group. A warning belongs to the
group of a given engine if only that engine manifests distinct
behavior, \ie{}, it produces a distinct output compared to others. We
separated in a distinct group the warnings for which two engines
diverge. The rationale for this methodology was to give attention to
each engine more uniformly, enabling more fair comparison across
engines.

\vspace{0.5ex}
\subsubsection{Results} In this section we discuss results obtained
across these two phases of the experiment. Table~\ref{tab:summary-lo}
shows statistics of \lo\ warnings obtained when fuzzing inputs with
different tools. Column ``\# buckets'' shows the number of buckets
associated with ``\lo'' warnings, column ``\# files'' shows the total
number of files involved in these warnings, and column ``avg. \# files
per bucket'' show the average number of files per bucket. Note that,
although the number of buckets and files differ substantially across
fuzzers, the difference of files per bucket was negligible.

@@

Table~\ref{tab:summary-hi} shows statistics of \hi\ warnings; recall
from Section~\ref{sec:clusterization} that we do not cluster
\hi\ warnings\Comment{ as there was no clear clustering criteria to
  use for that}. This table breaks down \hi\ warning by the affected
engine, \ie, the engine manifesting distinct output among those
analyzed. Column ``+1'' show the cases where more than one engine
disagree on the output. Note that the ordering of engines considering
this metric is consistent with the one observed on
Table~\ref{tab:cross-testing}, with \chakra\ and \jsc\ holding first
and second place, respectively, in number of warnings (resp.,
failures) compared to other engines.
%\veight\ and \smonkey.

@@

Table~\ref{tab:false-positives} shows the distribution of false
positives per source. The sources of imprecision are as defined in
Section~\ref{sec:transplantation} with the addition of three new
sources, which we did not observe before. These sources are
highlighted with a ``*'' in the table. The source ``Invalid Input''
indicates that the test input violated some part of the
specification. For example, the test indirectly invoked some function
with unexpected arguments; this happens because fuzzing is not
sensitive to function specifications. The source ``Upcoming Feature''
indicates that the test fails because it uses a feature that is
available in the original engine, but it is still not standard, and
the target engine does not support that feature. For example,
\Fix{provide concrete example}. \Fix{explain error message mismatch}

\begin{table}[h]
  \centering
  \caption{\label{tab:false-positives}Distribution of false
    positives buckets per source.}
  \begin{tabular}{crr}
    \toprule
    & \radamsa\ & \quickfuzz\ \\
    Undefined Behavior & 18 & - \\
    Timeout/OME & 23 & - \\
    Not Implemented & 19 & - \\
    * Invalid Input & 10 & - \\    
    * Upcoming Feature & - & - \\
    * Error Message Mismatch & 3 & - \\        
    \bottomrule     
  \end{tabular}
\end{table}

Table~\ref{tab:bugs} shows the list of bugs we reported. The table is
organized in two sections. The top section shows results obtained
during the exploratory phase of the study and the bottom section shows
the results obtained during the non-exploratory phase. The table shows
the date the bug was reported (``Date''), the fuzzing tool used
(``Fuzz''), the \js\ engine affected (``Engine''), the status of the
bug report as of Aug. 24, 2018 (``Status''), the Url of the bug report
(``Url''), the severity of the bug report (``Severity''), the priority
that we assigned to the warning that revealed the bug (``Priority''),
and the test suite from the original test input (``Suite'').

So far, ten of the bugs we reported were confirmed, two of
which were fixed. One bug report we submitted was rejected on the
basis that the offending JS file manifested an incompatibility across
engine implementations that was expected.  Note from the table that
all bug reports still waiting for confirmation are associated with the
\jsc{} engine. A closer look at the \jsc{} issue tracker showed that
their triage process is slow relative to \chakra's.\Comment{\Igor{ The bugs
  reported on \chakra{}'s bug tracker was defined as confirmed,
  however the bugs are included on a milestone for the next release
  following an internal priority.  }} As of now, we did not find any
new bug on \smonkey{} and V8; the bugs we found were duplicates and
were not reported.

%% Finally, it is worth noting that \Fix{11 of the 19}
%% JS files that manifested discrepancies were \emph{not} produced with
%% fuzzing (column ``Fuzz''). These are test files from suites of
%% different engines. This observation emphasizes the importance of
%% continuously collecting test suites from multiple sources; today, we
%% use test suites from seven different open source engines, including a
%% total of 30K test files.
